---
title: "rimgtool-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rimgtool-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction to rimgtool

This package provides three functions:
- sharpen
- compress
- shrink

As the name suggests, we aim to providing some tools for easy image processing.  To use this package, follow the installation guide on README and install this package.  Then, import the package.

```{r setup}
library(rimgtool)
```

## Shrpen function

The purpose of this function is to detect and enhance the edges in a grey-scale image using a 2-D convolution.  To demonstrate how it works, we first load a image of our respectful program director.

```{r 1.1, fig.width=15, fig.height=10}
img <- png::readPNG("../img/milad_cropped.png")
plot.new()
rasterImage(img[, , 1], 0, 0, 0.5, 1)
```

Then, we pass the image into the `sharpen()` function and get an edge-enhanced back.  We can compare the two images, and it is obvious that the wrinkles and hair of the photo below have more details.

```{r 1.3 test, fig.width=15, fig.height=10}
img2 <- sharpen(img)
plot.new()
rasterImage(img2, 0, 0, 0.5, 1)
```
